### 2019-06-12 doc/chapters/towards_verifying_addition.tex
ore explanation

As described before, Stainless supports only a subset of Scala.
The BigInt from the Stainless library is a bit restricted.
It does not support dynamic BigInt construction.
Only from literal arguments.

@@

This would be really hard to refactor, because Bitcoin-S tries to be as much dynamic as possible so it can be used with other cryptocurrencies than bitcoins too.
Maybe it would even be impossible, because they need to parse a lot from the bitcoin network.

Luckily, we can use toBigInt on underlying directly instead of going over toLong.

>>>>

As described before, Stainless supports only a subset of Scala.
The BigInt from the Stainless library is a bit restricted.
One such restriction is, that BigInt does not support dynamic BigInt construction.
Thus, the constructor parameter of BitInt must be a literal arguments.

@@

This would be really hard to refactor, because Bitcoin-S tries to be as much dynamic as possible so it can be used with other cryptocurrencies than bitcoins.
Maybe it would even be impossible, because they need to parse dynamic values from the bitcoin network.

Luckily, we can use toBigInt on underlying directly instead of going over toLong.
So, instead of converting the underlying to Long and and back to BigInt we convert underlying directly to BigInt.
